Data Analytics Introduction Using Python Training

### 2024-11-20 MsaPythonDataAnalytics.qmd
'update6'
'update7'

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: true
    scrollable: true
    incremental: false
    transition: concave
    background-transition: fade
    controls: true
    code-fold: true
    code-tools: true

@@

@@

>>>>

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: false
    scrollable: true
    incremental: false
    transition: concave
    background-transition: fade
    controls: true
    code-fold: true
    code-tools: true

@@

### Plotnine

<iframe class="stretch" data-src="https://plotnine.org/reference/geom_point.html#basic-scatter-plot"></iframe>

@@

# Bonus Material

<iframe class="stretch" data-src="https://docs.google.com/presentation/d/16T9NAqRoLzOy1h5PtO_uoHN2lE037w9o/edit#slide=id.p1"></iframe>

<iframe class="stretch" data-src="https://docs.google.com/presentation/d/1ONt4y1iNkKB0bEZXBqucG--xwOIcoE8R/edit#slide=id.p1"></iframe>

<iframe class="stretch" data-src="https://pandas.pydata.org/pandas-docs/stable/user_guide/10min.html"></iframe>
